Aerospace applications are composed of many dynamic systems which are coupled, nonlinear, and difficult to
control. Fuzzy logic (FL) systems  provides a means by which to encode expert knowledge into a set of rules
which can produce highly nonlinear control signals; this is possible because FL, like many other soft
computational methods is a universal approximator. While FL systems alone excel at encapsulating expert
knowledge bases, when coupled with genetic algorithms (GA), they can learn the knowledge base from
evolutionary repetition. It is the goal of this work to present the efficacy of hybrid genetic fuzzy systems
(GFS) in a variety of applications. This will be achieved through exploring three specific use cases.

First, a variation of a benchmark problem presented at the 1990 American Control Conference is used to
demonstrate the robustness of FL control as well as the utility of GAs in the learning process. The results
are a controller that is far more resistant to even large changes in the plant dynamics compared to a linear
controller and a process by which a class of controllers may be quickly tuned for changes to the plant system.

The next problem applies the same approach to an elevator actuator for pitch control of an F-4 Phantom. This
controller is tuned for a nominal case and ten subjected to the same plant with degraded aerodynamic
coefficients. It is compared to a well-tuned PID controller.

The effort culminates in a practical application of a FL system to guide a small unmanned aerial system (sUAS)
to a precision landing on a target platform moving with uncertain velocity. This was accomplished using
custom developed Python software for GFS control in conjunction with Robot Operating System (ROS) and a
simulation environment called Gazebo. Heavy emphasis was placed on using only software components which can be
easily implemented on popular hardware platforms. ROS was critical to meeting this goal, as well as the open
source flight controller project PX4. A controller is presented which is capable of exerting the control
necessary to guide the vehicle to a successful landing on both a static and moving platform.
